Gravitational wave sensitivity curves

### 2014-07-29 Typesofsource.tex
h_rss again

As discussed in \ref{sec:insp}, the expected relation between $h_\mathrm{c}(f)$ and a typical waveform $\tilde{h}(f)$ is
\begin{equation}\label{eq:simple} 
h_\mathrm{c}(f) = \left|\tilde{h}(f)\right|\sqrt{{N}_{\mathrm{cycles}}} \; , 
\end{equation}
where ${N}_{\mathrm{cycles}}$ is the number of cycles of radiation generated by the source, which is of order unity for bursts. Due to the uncertainty of burst models, the waveform is commonly indicated by a constant amplitude across some finite bandwidth. This is analogous to computing the root-sum-square of the waveform polarisations
\begin{equation}
h_\mathrm{rss} = \sqrt{\int{|h_+(t)|}^2 + {|h_\times(t)|}^2\,\rmd t},
\end{equation}
which is a quantity that is used to characterise the sensitivity of detectors to bursts \citep{Bursts}. In this work, we favour a constant $h_\mathrm{c}(f)$ over $h_\mathrm{rss}$ for consistency with the other types of source.

>>>>

As discussed in \ref{sec:insp}, the expected relation between $h_\mathrm{c}(f)$ and a typical waveform $\tilde{h}(f)$ is
\begin{equation}\label{eq:simple} 
h_\mathrm{c}(f) = \left|\tilde{h}(f)\right|\sqrt{{N}_{\mathrm{cycles}}} \; , 
\end{equation}
where ${N}_{\mathrm{cycles}}$ is the number of cycles of radiation generated by the source, which is of order unity for bursts.

An alternative characterisation of the signal amplitude commonly used for burst sources is the root-sum-square of the waveform polarisations
\begin{equation}
h_\mathrm{rss} = \sqrt{\int{|h_+(t)|}^2 + {|h_\times(t)|}^2\,\rmd t}.
\end{equation}
If $\tilde{h}(f) = \tilde{h}$ is constant across the bandwidth $\Delta f$ then they are related by
\begin{equation}
h_\mathrm{rss} \simeq |\tilde{h}|\sqrt{\Delta f}.
\end{equation}
In this work, we favour a constant $h_\mathrm{c}(f)$ rather than $h_\mathrm{rss}$ for consistency with the other types of source.
